Demo arXiv template

### 2022-10-18 paper/paper.qmd
a draft on section what's the problem with current index construction

*indices constructed separately, but there are lots of are same [!], but hard to see from the current construction. "messy data are messy in there own way". Describe how they are same, so we can modular them*

There has not yet been a standardised workflow on index construction. 
For simple indices, users may be able to work out the calculation from the equations or workflow provided, while for more complicated construction, software is not even available for open-source consumption.
Even when the software implementation is available, most indices are computed through a single index command, [given examples but not too domain specific]. 
This software design focuses on the name of the index and includes all the steps in a single index function. 
With this design, there is little room for modification. For example, fit a new distribution that is not provided in the initial code. 
Also, when scaled to a large number of indices, it increases the cognitive load of remembering hundreds of index names. 
A better approach is to modularise these steps and construct a pipeline for users to build indices through choosing different building blocks from each module.
With this design, users focus on the operations involved in the index construction.
If an operation from another index is useful, users can borrow it to modify an existing index.

@@

- transparency: official published, can decompose the indices, 
- allow for calculation on uncertainty with randomization, 
- compare indices,
- tweak/ swap building blocks, 
- create new indices based on combinations of existing steps.

>>>>

*From last week: indices constructed separately, but there are lots of are same [!], but hard to see from the current construction. "messy data are messy in there own way". Describe how they are same, so we can modular them*

Currently, index construction lacks structure. 
It is often up to the researchers to decide whether to provide open source code on the new indices, what would be the best user interface for the new indices, and how easily the new indices can be used by end users, along with other existing indices. 
This causes the problem that indices are often designed separately and many indices simply lump all the steps into a [single command function]. 
While this simplifies the amount of code needed to derive index values from a set of inputs, many problems arise when the code is adopted outside the research group that wrote the index. 
First of all, indices created by a single command provide little room for modification.
For example, many indices involve a step to fit variables into a particular distribution.
Index researchers may provide options for different fits, but it is generally hard to experiment with options outside the provided distributions.
Also, many indices share similar or identical steps in part of their construction, a [single command function] eliminates the possibility to borrow codes written by others and forces researchers to rebuild the wheels when creating new indices.
Lastly, users may wish to inspect intermediate results during the index construction to validate the output or to compare results with other indices, but [single command functions] do not support this demand unless the users can customise the source code as they need.

<!-- indices are constructed separately in this design. -->
<!-- Many steps are more or less similar when constructing indices, but this would be hard to observe from the current construction.  -->
<!-- For example, many indices needs standardisation in its workflow, it can be used to rescale the input variables or the index series. -->
<!-- But the current construction does not make it clear through its user interface but sweep it, along with all the other steps in the index construction, under a single function call.  -->

<!-- There has not yet been a standardised workflow on index construction.  -->
<!-- For simple indices, users may be able to work out the calculation from the equations or workflow provided, while for more complicated construction, software is not even available for open-source consumption. -->
<!-- Even when the software implementation is available, most indices are computed through a single index command, [given examples but not too domain specific].  -->
<!-- This software design focuses on the name of the index and includes all the steps in a single index function.  -->
<!-- With this design, there is little room for modification. For example, fit a new distribution that is not provided in the initial code.  -->
<!-- Also, when scaled to a large number of indices, it increases the cognitive load of remembering hundreds of index names.  -->
<!-- A better approach is to modularise these steps and construct a pipeline for users to build indices through choosing different building blocks from each module. -->
<!-- With this design, users focus on the operations involved in the index construction. -->
<!-- If an operation from another index is useful, users can borrow it to modify an existing index. -->

Ideally each command corresponds to a user action

While jumbled indices jumble in their own ways, perspicuous indices are all alike. 
A clear pipeline for indices construction brings transparency to the algorithm. 
Many often, official websites like National Oceanic and Atmospheric Administration (NOAA) will regularly updates the raw data and the indices calculated for users' consumption and provides description of the methodology. 
However, the source code and the scripts is usually not publicly available and there is no tool, or users need to be its own tool, to verify the calculation. 
Once a data pipeline is built, users can follow the steps in the index construction to validate the numbers published by the authorities. 
Once a data pipeline is constructed, it opens possibility to do statistics on indices.
For example, bootstrap and other methods could be applied into the pipeline to calculate uncertainty on the index value with randomisation. 
Properties of existing indices can be examined through swapping the steps involved in the construction. 
For example, some indices prefer to standardise the input variables in the beginning of the workflow while other prefer to move the standardisation towards the end and directly apply it on the index value. 
A flexible pipline approach gives the freedom to construct the index in both ways by placing the standardisation step in different stages of the pipeline. 
The importance of the position of a single steps can be compared through indices constructed by placing the step at different stages of the pipeline. 
Also, the pipeline approach motivates new indices through combining existing steps from different indices.

<!-- - transparency: official published, can decompose the indices,  -->
<!-- - allow for calculation on uncertainty with randomization,  -->
<!-- - compare indices, -->
<!-- - tweak/ swap building blocks,  -->
<!-- - create new indices based on combinations of existing steps. -->

@@

### 2022-10-18 paper/paper.tex
a draft on section what's the problem with current index construction

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, borderline west={3pt}{0pt}{shadecolor}, interior hidden, enhanced, boxrule=0pt, breakable, frame hidden]}{\end{tcolorbox}}\fi

@@

\emph{indices constructed separately, but there are lots of are same
{[}!{]}, but hard to see from the current construction. ``messy data are
messy in there own way''. Describe how they are same, so we can modular
them}

There has not yet been a standardised workflow on index construction.
For simple indices, users may be able to work out the calculation from
the equations or workflow provided, while for more complicated
construction, software is not even available for open-source
consumption. Even when the software implementation is available, most
indices are computed through a single index command, {[}given examples
but not too domain specific{]}. This software design focuses on the name
of the index and includes all the steps in a single index function. With
this design, there is little room for modification. For example, fit a
new distribution that is not provided in the initial code. Also, when
scaled to a large number of indices, it increases the cognitive load of
remembering hundreds of index names. A better approach is to modularise
these steps and construct a pipeline for users to build indices through
choosing different building blocks from each module. With this design,
users focus on the operations involved in the index construction. If an
operation from another index is useful, users can borrow it to modify an
existing index.

@@

\begin{itemize}
\tightlist
\item
  transparency: official published, can decompose the indices,
\item
  allow for calculation on uncertainty with randomization,
\item
  compare indices,
\item
  tweak/ swap building blocks,
\item
  create new indices based on combinations of existing steps.
\end{itemize}

>>>>

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, interior hidden, borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt, sharp corners, frame hidden, enhanced]}{\end{tcolorbox}}\fi

@@

\emph{From last week: indices constructed separately, but there are lots
of are same {[}!{]}, but hard to see from the current construction.
``messy data are messy in there own way''. Describe how they are same,
so we can modular them}

Currently, index construction lacks structure. It is often up to the
researchers to decide whether to provide open source code on the new
indices, what would be the best user interface for the new indices, and
how easily the new indices can be used by end users, along with other
existing indices. This causes the problem that indices are often
designed separately and many indices simply lump all the steps into a
{[}single command function{]}. While this simplifies the amount of code
needed to derive index values from a set of inputs, many problems arise
when the code is adopted outside the research group that wrote the
index. First of all, indices created by a single command provide little
room for modification. For example, many indices involve a step to fit
variables into a particular distribution. Index researchers may provide
options for different fits, but it is generally hard to experiment with
options outside the provided distributions. Also, many indices share
similar or identical steps in part of their construction, a {[}single
command function{]} eliminates the possibility to borrow codes written
by others and forces researchers to rebuild the wheels when creating new
indices. Lastly, users may wish to inspect intermediate results during
the index construction to validate the output or to compare results with
other indices, but {[}single command functions{]} do not support this
demand unless the users can customise the source code as they need.

Ideally each command corresponds to a user action

While jumbled indices jumble in their own ways, perspicuous indices are
all alike. A clear pipeline for indices construction brings transparency
to the algorithm. Many often, official websites like National Oceanic
and Atmospheric Administration (NOAA) will regularly updates the raw
data and the indices calculated for users' consumption and provides
description of the methodology. However, the source code and the scripts
is usually not publicly available and there is no tool, or users need to
be its own tool, to verify the calculation. Once a data pipeline is
built, users can follow the steps in the index construction to validate
the numbers published by the authorities. Once a data pipeline is
constructed, it opens possibility to do statistics on indices. For
example, bootstrap and other methods could be applied into the pipeline
to calculate uncertainty on the index value with randomisation.
Properties of existing indices can be examined through swapping the
steps involved in the construction. For example, some indices prefer to
standardise the input variables in the beginning of the workflow while
other prefer to move the standardisation towards the end and directly
apply it on the index value. A flexible pipline approach gives the
freedom to construct the index in both ways by placing the
standardisation step in different stages of the pipeline. The importance
of the position of a single steps can be compared through indices
constructed by placing the step at different stages of the pipeline.
Also, the pipeline approach motivates new indices through combining
existing steps from different indices.

@@
